\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-05-01 jss/article.tex
changes

\section[Examples]{Examples}
\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease (hopefully not). If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery. On top of that, if you can figure out each hospital's abililty to handle this surgery, it will be useful for your decision to choose a hospital.
\\

@@

For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.834$) was calculated by 336 / (336 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.834)*0.045 + 0.834 * 0.020=0.024$. As for this hospital, using more information from the prior distribution makes sense because its observed amount of information (67) is far less than the amount of state-level information (336).
\\

@@

Intuitively, the result of multilevel modeling makes more sense than that of naive sample mean. For example, suppose there are two hospitals, whose sample means ($z_{j} / n_{j}$) are 0 and 0.01 and caseloads ($n_{j}$) are 1 and 100 each. Do you believe that the former hospital is better than the latter and are you going to choose the former hospital? Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload. Though somewhat extreme, this is what happened to the two left-most hostpitals in the first plot and this is why hierarchical modeling is a reasonable choice for this data set.
\\

The estimated 95\% intervals are displayed on the right-side plot. We can clearly see that all the posterior means (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line). For reference, if we want to draw this plot by the order of data input, \code{plot(p, sort = FALSE)} is a right adjustment. Overall, as the caseload (size of dots) increases towards the right and as the posterior mean gets closer to 0, the length of interval gets shorter, which the formula of posterior variance in (6) implies. But the most important information from this plot would be the visualized range of each hospital's true death rate per exposure. 
\\

This plot can add one more valuable point, which we could not have noticed, to the previous plot based mostly on point estimates. Let's look at the 8th and the 31st hospitals on the graph (or on the outcome for numeric reference). The point estimate of the true death rate per exposure of the 31st hospital is higher than the one of the 8th. But, the upper bound of interval estimate of this 31st hospital is lower than that of the 8th. This interval plot makes the 31st hospital emerge as one of your candidates. (Could you regard this 31st hospital as a possible candidate before you observe this plot?)
\\

@@

Then, how reliable are these intervals? Does our procedure to generate interval estimates have good repeated sampling property? The following method check will answer this question. The \code{coverage} function below generates 10,000 pseudo-data sets assuming the estimated $r~(=336.37)$ as a given value. For reference, we can try any other value of $r$, for example $r=200$, by replacing below code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
\\

Also, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is \code{R> p <- gbp(z, n, Alpha = 0.9, model = "pr")}.  Then, the function \code{coverage} will evaluate whether interval estimates achieve 90\% confidence level.
\\

@@

It estimated coverage probabilities by unbiased estimates (a blue dashed line) and Rao-Blackwellized estimates (a red line). Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 from the Rao-Blackwellized estimate and 0.95 from the unbiased estimate. Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular data set has a very good repeated sampling property.
\\

>>>>

\section[Examples]{Examples}
\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease (hopefully not). If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery. On top of that, if you can figure out each hospital's abililty to handle this surgery, it will be useful for your decision in choosing a hospital.
\\

@@

For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.834$) was calculated by 336 / (336 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.834)*0.045 + 0.834 * 0.020=0.024$. As for this hospital, using more information from the prior distribution is a sensible choice because its observed amount of information (67) is far less than the amount of state-level information (336).
\\

@@

Intuitively, the result of multilevel modeling makes more sense than that of naive sample mean. For example, suppose there are two hospitals, whose sample means ($z_{j} / n_{j}$) are 0 and 0.001 and caseloads ($n_{j}$) are 1 and 1000 each. Do you believe that the former hospital, whose observed death rate is 0, is better than the latter and are you going to choose the former hospital? Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload. Though somewhat extreme, this is what happened to the two left-most hostpitals in the first plot and this is why hierarchical modeling is a reasonable choice for this data set.
\\

The estimated 95\% intervals are displayed on the right-side plot. We can clearly see that all the posterior means (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line). For reference, if we want to draw this plot by the order of data input, \code{plot(p, sort = FALSE)} is a right adjustment. Overall, as the caseload increases towards the right and as the posterior mean gets closer to 0, the length of interval gets shorter, which the formula of posterior variance in (6) implies. 
\\

This interval plot can give us one more valuable insight, which we could not have noticed. Let's look at the 8th and the 31st hospitals on the graph (or on the outcome for numeric reference). The point estimate of the true death rate per exposure of the 31st hospital is higher than the one of the 8th. But, the upper bound of interval estimate of this 31st hospital is lower than that of the 8th. This interval plot makes the 31st hospital emerge as one of your candidates. (Could you regard this 31st hospital as a possible candidate before you observe this plot?)
\\

@@

Then, how reliable are these intervals? Does our procedure to generate interval estimates have good repeated sampling property? The following method check will answer this question. The \code{coverage} function below generates 10,000 pseudo-data sets regarding the estimated $r~(=336.37)$ as a given true value. For reference, we can try any other value of $r$, for example $r=200$, by replacing below code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
\\

Also, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is \code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "pr")}.  Then, the function \code{coverage} will evaluate whether interval estimates achieve 90\% confidence level.
\\

@@

It estimated coverage probabilities by simple unbiased estimates (a blue dashed line) and Rao-Blackwellized unbiased estimates (a red line). Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 from the Rao-Blackwellized estimate and 0.95 from the simple unbiased estimate. Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular data set has nice repeated sampling property.
\\
